Meta-analysis

### 2019-09-15 05_MetaAnalysis.Rmd
Use import_data() function

```{r MEsummary_Libraries, message=FALSE}
library(tidyverse)
library(theme.usq)
```

@@

```{r data_import, message=FALSE, echo=FALSE}
PM_MB_means <-
   read_csv(
      "data/1902 powdery mildew-Mungbean - Collated means.csv"
   )

# convert coltypes
PM_MB_means <-
   PM_MB_means %>%
   mutate(year = as.integer(year)) %>%
   mutate(replicates = as.integer(replicates)) %>%
   mutate(planting_date = as.Date(planting_date, format = "%d/%m/%Y")) %>%
   mutate(emergence_date = as.Date(emergence_date, format = "%d/%m/%Y")) %>%
   mutate(flowering_date = as.Date(flowering_date, format = "%d/%m/%Y")) %>%
   mutate(pod_final_date = as.Date(pod_final_date, format = "%d/%m/%Y")) %>%
   mutate(mid_late_pod_final = as.Date(mid_late_pod_final, format = "%d/%m/%Y")) %>%
   mutate(first_sign_disease = as.Date(first_sign_disease, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_1 = as.Date(fungicide_application_1, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_2 = as.Date(fungicide_application_2, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_3 = as.Date(fungicide_application_3, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_4 = as.Date(fungicide_application_4, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_5 = as.Date(fungicide_application_5, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_6 = as.Date(fungicide_application_6, format = "%d/%m/%Y")) %>%
   mutate(fungicide_application_7 = as.Date(fungicide_application_7, format = "%d/%m/%Y")) %>%
   mutate(harvest_date = as.Date(harvest_date, format = "%d/%m/%Y")) %>%
   mutate(final_assessment = as.Date(final_assessment, format = "%d/%m/%Y"))
```

>>>>

```{r MEsummary_Libraries, message=FALSE}
library(tidyverse)
library(theme.usq)
source("R/import_data.R")
```

@@

```{r data_import, message=FALSE, echo=FALSE}
PM_MB_means <- import_data()
```
